 ---
 title: "Experiment_2"
 author: "Andrew Ithurburn"
 date: "11/05/2021"
 output: 
   html_document:
     toc: yes
     toc_float:
       smooth_scroll: yes
     code_folding: hide
     fig_caption: yes
     number_sections: yes
     css: table_styling.css
 editor_options: 
   chunk_output_type: console
 ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DT)
library(ggplot2)
library(ggthemes)
library(tidyverse)
library(papaja)
library(brms)
library(rstan)
library(bayestestR)
library(sjPlot)
library(psych)
library(BayesFactor)
library(bayesplot)
library(kableExtra)


library(ggcorrplot)
library(ggprism)

options(mc.corrs = parallel::detectCores()) # can run chains in parallel with each other
rstan_options(auto_write = TRUE)
options(control = list(adapt_delta = 0.99999))
options(brms.backend = "cmdstanr")

bayesplot::bayesplot_theme_set(theme_apa())
locfunc <- function(data, to){
  which(colnames({{data}})=={{to}})
}

lfunc <- function(dataset, to, from) {
  loc1 <- which(colnames({{dataset}}) == {{to}})
  loc2 <- which(colnames({{dataset}}) == {{from}})
  length({{dataset}}[loc1:loc2])
}
theme_set(theme_apa(base_size = 12))

```

## Cleanup

```{r, cleanup, message=FALSE, warning=FALSE}
experiment_two_DS_time <- read.csv("Experiment_2_Dataset_clean.csv")
experiment_two_DS <- read.csv("Experiment_2_Dataset_clean_noTime.csv")
m2prior <- readRDS("m2prior.rds")
corr_table <- readRDS("corr_table.rds")
m4 <- readRDS("m4.rds")
m5 <- readRDS("m5.rds")
m5_gen <- readRDS("m5_gen.rds")
m7 <- readRDS("m7.rds")
m8 <- readRDS("m8.rds")
m8_gen <- readRDS("m8_gen.rds")
m8_Age <- readRDS("m8_Age.rds")
dm0 <- readRDS("dm0.rds")
dm1 <- readRDS("dm1.rds")
dm2 <- readRDS("dm2.rds")
dm3 <- readRDS("dm3.rds")
dm4 <- readRDS("dm4.rds")
dm5 <- readRDS("dm5.rds")
demographicQuestions <- c("Age", "Gender", "Ethnicity", "Eth.ori", "Edu")
sjsQuestions <- c("SJS.1", "SJS.2", "SJS.3")
srpsQuestions <- c("SRPS.1"
, "SRPS.2"
, "SRPS.3"
, "SRPS.4"
, "SRPS.5"
, "SRPS.6"
, "SRPS.7"
, "SRPS.8"
, "SRPS.9"
, "SRPS.10"
, "SRPS.11"
, "SRPS.12"
, "SRPS.13"
, "SRPS.14"
, "SRPS.15"
, "SRPS.17"
, "SRPS.18"
, "SRPS.19"
, "SRPS.20"
, "SRPS.21"
, "SRPS.22"
, "SRPS.23"
, "SRPS.24")

srps.rcQuestions <- c("SRPS.1"
, "SRPS.2"
, "SRPS.3"
, "SRPS.4"
, "SRPS.5"
, "SRPS.6"
, "SRPS.7"
, "SRPS.8"
, "SRPS.9"
, "SRPS.10"
, "SRPS.11"
, "SRPS.12"
, "SRPS.13"
, "SRPS.14"
, "SRPS.15")

srps.dmQuestions <- c("SRPS.17"
, "SRPS.18"
, "SRPS.19"
, "SRPS.20"
, "SRPS.21"
, "SRPS.22"
, "SRPS.23"
, "SRPS.24")

ssesQuestions <- c("SSES.1"
, "SSES.2"
, "SSES.3"
, "SSES.4"
, "SSES.5"
, "SSES.6"
, "SSES.7"
, "SSES.8"
, "SSES.9"
, "SSES.10")


spiteQuestions <- c("Spite.1"
, "Spite.2"
, "Spite.3"
, "Spite.4"
, "Spite.5"
, "Spite.6"
, "Spite.7"
, "Spite.8"
, "Spite.9"
, "Spite.10"
, "Spite.11"
, "Spite.12"
, "Spite.13"
, "Spite.14"
, "Spite.15"
, "Spite.16")


Vign.Sex <- c("Vign.1", "Vign.2", "Vign.4", "Vign.7", "Vign.10")
Vign.noSex <- c("Vign.3", "Vign.5", "Vign.6", "Vign.8", "Vign.9")
Vign.Overall <- c("Vign.1", "Vign.2", "Vign.4", "Vign.7", "Vign.10", "Vign.3", "Vign.5", "Vign.6", "Vign.8", "Vign.9")

Real.Sex <- c("Real.1", "Real.2", "Real.4", "Real.7", "Real.10")
Real.noSex <- c("Real.3", "Real.5", "Real.6", "Real.8", "Real.9")
Real.Overall <- c("Real.1", "Real.2", "Real.4", "Real.7", "Real.10", "Real.3", "Real.5", "Real.6", "Real.8", "Real.9")

doplQuestions <- c('DoPL_1', 'DoPL_6', 'DoPL_11', 'DoPL_13', 'DoPL_14', 'DoPL_16', 'DoPL_5', 'DoPL_7', 'DoPL_8', 'DoPL_12', 'DoPL_17', 'DoPL_18', 'DoPL_2', 'DoPL_3', 'DoPL_4', 'DoPL_9', 'DoPL_10', 'DoPL_15')

dominanceQuestions <- c('DoPL_2','DoPL_3','DoPL_4','DoPL_9','DoPL_10','DoPL_15')
prestigeQuestions <- c('DoPL_5','DoPL_7','DoPL_8','DoPL_12','DoPL_17','DoPL_18')
leadershipQuestions <- c('DoPL_1','DoPL_6','DoPL_11','DoPL_13','DoPL_14','DoPL_16')

UMSQuestions <- c('UMS_1', 'UMS_2', 'UMS_3', 'UMS_4','UMS_5','UMS_6','UMS_7','UMS_8','UMS_9','UMS_11', 'UMS_12')
UMSIntimacyQuestions <- c('UMS_11', 'UMS_12')
UMSAffiliationQuestions <- c('UMS_1', 'UMS_2', 'UMS_3', 'UMS_4','UMS_5','UMS_6','UMS_7','UMS_8','UMS_9')

savedQuestionsBefore <- c('subjectID', "Age", "Duration..in.seconds.", "Gender", "Ethnicity", "Eth.ori", "Edu",
                     "DoPLSum"
,"dominanceSum"
,"prestigeSum"
,"leadershipSum"
,"UMSSum"
,"UMSIntimacySum"
,"UMSAffiliationSum"
,"sjsSum"
,"ssesSum"
, "Spite"
,"Vign.Sex"
,"Vign.noSex"
,"Vign.Ovr.Score"
,"Real.Sex"
,"Real.noSex"
,"Real.Ovr.Score"
,"srps.rc.rescale"
,"srps.dm.rescale"
,"srps.sum.rescale",
"Power",
"Vign.1",
"Vign.2",
"Vign.3",
"Vign.4",
"Vign.5",
"Vign.6",
"Vign.7",
"Vign.8",
"Vign.9",
"Vign.10",
"Real.1",
"Real.2",
"Real.3",
"Real.4",
"Real.5",
"Real.6",
"Real.7",
"Real.8",
"Real.9",
"Real.10")

savedQuestionsAfter <- c('subjectID', "Age", "Duration..in.seconds.", "Gender", "Ethnicity", "Eth.ori", "Edu",
                     "DoPLSum"
,"dominanceSum"
,"prestigeSum"
,"leadershipSum"
,"UMSSum"
,"UMSIntimacySum"
,"UMSAffiliationSum"
,"sjsSum"
,"ssesSum"
, "Spite"
,"Vign.Sex"
,"Vign.noSex"
,"Vign.Ovr.Score"
,"Real.Sex"
,"Real.noSex"
,"Real.Ovr.Score"
,"srps.rc.rescale"
,"srps.dm.rescale"
,"srps.sum.rescale"
,"Content",
"Vignette",
"Justification",
"Realism",
"Power")
```

## Recoding variables
```{r recoding variables, message=FALSE, warning=FALSE}

write.csv(experiment_two_DS, "new_DF.csv")
  
  
```

## Summing data

```{r, message=FALSE, warning=FALSE}
# DOPL----
experiment_two_DS$DoPLSum  <- rowSums(experiment_two_DS[, doplQuestions])
experiment_two_DS$dominanceSum <-
  rowSums(experiment_two_DS[, dominanceQuestions])
experiment_two_DS$prestigeSum <-
  rowSums(experiment_two_DS[, prestigeQuestions])
experiment_two_DS$leadershipSum <-
  rowSums(experiment_two_DS[, leadershipQuestions])

# UMS----
experiment_two_DS$UMSSum  <- rowSums(experiment_two_DS[, UMSQuestions])
experiment_two_DS$UMSIntimacySum  <- rowSums(experiment_two_DS[, UMSIntimacyQuestions])
experiment_two_DS$UMSAffiliationSum  <- rowSums(experiment_two_DS[, UMSAffiliationQuestions])

# Spite ----

experiment_two_DS$Spite  <- rowSums(experiment_two_DS[, spiteQuestions])

# SJS----
experiment_two_DS$sjsSum <- rowSums(experiment_two_DS[, sjsQuestions])

# SSES----
experiment_two_DS$ssesSum <- rowSums(experiment_two_DS[, ssesQuestions])

# Vign----
experiment_two_DS$Vign.Sex <- rowSums(experiment_two_DS[, Vign.Sex])
experiment_two_DS$Vign.noSex <- rowSums(experiment_two_DS[, Vign.noSex])
experiment_two_DS$Vign.Ovr.Score <- rowSums(experiment_two_DS[, Vign.Overall])

# Realism----
experiment_two_DS$Real.Sex <- rowSums(experiment_two_DS[, Real.Sex])
experiment_two_DS$Real.noSex <- rowSums(experiment_two_DS[, Real.noSex])
experiment_two_DS$Real.Ovr.Score <- rowSums(experiment_two_DS[, Real.Overall])

# SRPS----
experiment_two_DS$srps.rc.sum <- rowSums(experiment_two_DS[, srps.rcQuestions])
experiment_two_DS$srps.dm.sum <- rowSums(experiment_two_DS[, srps.dmQuestions])

# SRPS Rescaled----
experiment_two_DS$srps.rc.rescale <- ((experiment_two_DS$srps.rc.sum - 15)/(60 - 15)) * 3 + 1
experiment_two_DS$srps.dm.rescale <- ((experiment_two_DS$srps.dm.sum - 8)/(24 - 8)) * 3 + 1
experiment_two_DS$srps.sum <- ((experiment_two_DS$srps.dm.sum + experiment_two_DS$srps.rc.sum)/2)
experiment_two_DS$srps.sum.rescale <- ((experiment_two_DS$srps.sum - 11.5) / (42 - 11.5)) * 3 + 1

experiment_two_DS <- experiment_two_DS %>% mutate(Power = case_when(
  experiment_two_DS$srps.sum.rescale < 2.420 ~ "Low",
  experiment_two_DS$srps.sum.rescale > 2.420 & experiment_two_DS$srps.sum.rescale < 2.820   ~ "Medium",
  experiment_two_DS$srps.sum.rescale > 2.820 ~ "High"
))
```

## Renaming

```{r Experiment 2 dataset for analysis, message=FALSE, warning=FALSE}

experiment_two_DS <- rowid_to_column(experiment_two_DS, "subjectID")

newDF <- experiment_two_DS[savedQuestionsBefore]

analysisDF <- newDF %>%
  pivot_longer("Vign.1":"Vign.10", names_to = "Vignette", values_to = "Justification")
  
tester1 <- newDF %>%
  pivot_longer("Real.1":"Real.10", names_to = "Real", values_to = "Realism")

analysisDF['Realism'] = tester1["Realism"]



analysisDF <- analysisDF %>% mutate(Content = case_when(
 analysisDF$Vignette == "Vign.1" ~ "Sexual",
analysisDF$Vignette == "Vign.2" ~  "Sexual",
analysisDF$Vignette == "Vign.3" ~ "Nonsexual",
analysisDF$Vignette == "Vign.4" ~  "Sexual",
analysisDF$Vignette == "Vign.5" ~  "Nonsexual",
analysisDF$Vignette == "Vign.6" ~ "Nonsexual",
analysisDF$Vignette == "Vign.7" ~ "Sexual",
analysisDF$Vignette == "Vign.8" ~ "Nonsexual",
analysisDF$Vignette == "Vign.9" ~ "Nonsexual",
analysisDF$Vignette == "Vign.10" ~ "Sexual"
))

analysisDF <- analysisDF %>% mutate(Vignette = case_when(
 analysisDF$Vignette == "Vign.1" ~  1,
analysisDF$Vignette == "Vign.2" ~  2,
analysisDF$Vignette == "Vign.3" ~  3,
analysisDF$Vignette == "Vign.4" ~  4,
analysisDF$Vignette == "Vign.5" ~  5,
analysisDF$Vignette == "Vign.6" ~  6,
analysisDF$Vignette == "Vign.7" ~  7,
analysisDF$Vignette == "Vign.8" ~  8,
analysisDF$Vignette == "Vign.9" ~  9,
analysisDF$Vignette == "Vign.10" ~ 10
))

analysisDF <- analysisDF[, savedQuestionsAfter]

analysisDF <- analysisDF %>%
rename("subjectID" = "subjectID") %>%
rename("Duration" = "Duration..in.seconds.") %>%
rename("Age" = "Age") %>%
rename("Gender" = "Gender") %>%
rename("Ethnicity" = "Ethnicity") %>%
rename("Ethnic_Origin" = "Eth.ori") %>%
rename("Education" = "Edu") %>%
rename("DoPL" = "DoPLSum") %>%
rename("Dominance" = "dominanceSum") %>%
rename("Prestige" = "prestigeSum") %>%
rename("Leadership" = "leadershipSum") %>%
rename("UMS" = "UMSSum") %>%
rename("UMS_Intimacy" = "UMSIntimacySum") %>%
rename("UMS_Affiliation" = "UMSAffiliationSum") %>%
rename("SJS" = "sjsSum") %>%
rename("SSES" = "ssesSum") %>%
rename("Vign.Sex" = "Vign.Sex") %>%
rename("Vign.noSex" = "Vign.noSex") %>%
rename("Vign.Ovr.Score" = "Vign.Ovr.Score") %>%
rename("Realism_Sex" = "Real.Sex") %>%
rename("Realism_NoSex" = "Real.noSex") %>%
rename("Realism_Overall" = "Real.Ovr.Score") %>%
rename("SRPS_RC" = "srps.rc.rescale") %>%
rename("SRPS_DM" = "srps.dm.rescale") %>%
rename("SRPS" = "srps.sum.rescale") %>%
rename("Vignette" = "Vignette") %>%
rename("Justification" = "Justification") %>%
rename("Realism" = "Realism") %>%
rename("Content" = "Content")
```
## Fixing class

```{r Analysis, message=FALSE, warning=FALSE}
analysisDF$Vignette <- factor(analysisDF$Vignette)
analysisDF$subjectID <- factor(analysisDF$subjectID)
analysisDF$Spite_z <- scale(analysisDF$Spite)
analysisDF$SSES_z <- scale(analysisDF$SSES)
analysisDF$SRPS_z <- scale(analysisDF$SRPS)
analysisDF$SJS_z <- scale(analysisDF$SJS)
analysisDF$Justification_z <- scale(analysisDF$Justification)
analysisDF$Realism_z <- scale(analysisDF$Realism)
analysisDF$DoPL_z <- scale(analysisDF$DoPL)
analysisDF$Dominance_z <- scale(analysisDF$Dominance)
analysisDF$Leadership_z <- scale(analysisDF$Leadership)
analysisDF$Prestige_z <- scale(analysisDF$Prestige)
analysisDF$UMS_z <- scale(analysisDF$UMS)
analysisDF$UMS_Intimacy_z <- scale(analysisDF$UMS_Intimacy)
analysisDF$UMS_Affiliation_z <- scale(analysisDF$UMS_Affiliation)
```

## Basic gglots
```{r Basic ggplots, echo=TRUE, message=FALSE, warning=FALSE}
ggplot(analysisDF, aes(x = DoPL, y = Justification, color = Content)) + geom_point() + geom_smooth(method = "lm")
ggplot(analysisDF, aes(x = Dominance, y = Justification, color = Content)) + geom_point() + geom_smooth(method = "lm")
ggplot(analysisDF, aes(x = Leadership, y = Justification, color = Content)) + geom_point() + geom_smooth(method = "lm")
ggplot(analysisDF, aes(x = Prestige, y = Justification, color = Content)) + geom_point() + geom_smooth(method = "lm")

```

# Initial Bayesian Analysis
```{r}

```

```{r Bayesian, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}



m0 <- brm(Justification_z ~ 1 + (1|Vignette) + (1|subjectID), data = analysisDF, 
         warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 4, save_all_pars = T,
          prior = c(prior(normal(0,1), class = 'Intercept')))

# models 
m1 <- brm(Justification_z ~ Spite_z * Content + (1|Vignette) + (1|subjectID), data = analysisDF, 
        warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, save_all_pars = T,
         prior = c(prior(normal(0,1), class = 'Intercept'),
                   prior(normal(0,1), class = 'b'),
                   prior(normal(0.151, 0.0723), class = b, coef = "Spite_z:ContentSexual")))
summary(m1) 

m2 <- brm(Justification ~ Spite_z * Content + Realism_z + (1|Vignette) + (1|subjectID), data = analysisDF, 
        warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 4, save_all_pars = T,
         prior = c(prior(normal(0,1), class = 'Intercept'),
                   prior(normal(0,1), class = 'b'),
                   prior(normal(0.151, 0.0723), class = b, coef = "Spite_z:ContentSexual")))
summary(m2)

m3 <- brm(Justification ~ Spite_z * Content + Realism_z + SSES + SRPS + SJS + (1|Vignette) + 
           (1|subjectID), data = analysisDF,warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, 
         save_all_pars = T,
         prior = c(prior(normal(0,1), class = 'Intercept'),
                   prior(normal(0,1), class = 'b'),
                   prior(normal(0.151, 0.0723), class = b, coef = "Spite_z:ContentSexual")))
summary(m3)

m4 <- brm(Justification ~ Spite_z * Content * Realism_z + SSES_z + SRPS_z + SJS_z + (1|Vignette) + 
           (1|subjectID), data = analysisDF,warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, 
         save_all_pars = T,
         prior = c(prior(normal(0,1), class = 'Intercept'),
                   prior(normal(0,1), class = 'b'),
                   prior(normal(0.151, 0.0723), class = b, coef = "Spite_z:ContentSexual")))

```

### Bayesian Correlation

```{r, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
scale_corr <- brm(mvbind(SSES, SRPS, Spite, SJS, Dominance, Prestige, Leadership) ~ 1, data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6, 
                  prior = c(prior(normal(0, 1), class = "Intercept")), save_all_pars = T)
cor_1 <- summary(scale_corr)
corr_table <- cor_1[["rescor_pars"]]
```


```{r}
kable(corr_table, format = "html", booktabs = T, escape = F, longtabe = F, digits = 2, col.names = c('Estimate',	'Est.Error',	'l-95% CI',	'u-95% CI',	'Rhat',	'Bulk_ESS',	'Tail_ESS')) %>% 
  kable_styling(full_width = F)  %>%
 
```

### DoPL motives predicting risky behavior (by content) in addition to spitefulness

```{r Bayesian Analysis, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
dm0 <- brm(Justification ~ 1, data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = c(prior(normal(0, 1), class = "Intercept")), save_all_pars = T)

summary(dm0)

dm1 <- brm(Justification ~ Dominance_z * Gender + Prestige_z * Gender + Leadership_z * Gender + (1|Vignette) + (1|subjectID), data = analysisDF, iter = 8000,control = list(adapt_delta = 0.99), warmup = 500, chains = 4, cores = 6
           ,prior = c(prior(normal(0, 1), class = "Intercept"),
                      prior(normal(3, 1), class = "b", coef = "Dominance_z:Gender"),
                      prior(normal(0, 1), class = "b", coef = "Gender:Leadership_z"), 
                      prior(normal(0, 1), class = "b", coef = "Gender:Prestige_z"),
                      prior(normal(0, 1), class = "b", coef = "Dominance_z"),
                      prior(normal(0, 1), class = "b", coef = "Leadership_z"),
                      prior(normal(0, 1), class = "b", coef = "Prestige_z")), save_all_pars = T)

summary(dm1)

dm3 <- brm(Justification ~ Dominance_z * Gender + Prestige_z * Gender + Leadership_z * Gender + Age + (1|Vignette) + (1|subjectID), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = c(prior(normal(0, 1), class = "Intercept")), save_all_pars = T)

summary(dm3)

dm2 <- brm(Justification ~ Dominance_z * Gender + Prestige_z * Gender + Leadership_z * Gender + SJS_z + SRPS_z + SSES_z + Spite_z +  (1|Vignette) + (1|subjectID), control = list(adapt_delta = 0.99), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = c(prior(normal(0, 1), class = "Intercept"),
                      prior(normal(3, 1), class = "b", coef = "Dominance_z:Gender"),
                      prior(normal(0, 1), class = "b", coef = "Gender:Leadership_z"), 
                      prior(normal(0, 1), class = "b", coef = "Gender:Prestige_z"),
                      prior(normal(0, 1), class = "b", coef = "Dominance_z"),
                      prior(normal(0, 1), class = "b", coef = "Leadership_z"),
                      prior(normal(0, 1), class = "b", coef = "Prestige_z")), save_all_pars = T)

summary(dm2)

dm4 <- brm(Justification ~ Dominance_z * Gender * Content + Prestige_z * Gender * Content + Leadership_z * Gender * Content + SJS_z + SRPS_z + SSES_z + Spite_z +  (1|Vignette) + (1|subjectID), control = list(adapt_delta = 0.99), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = c(prior(normal(0, 1), class = "Intercept"),
                      prior(normal(3, 1), class = "b", coef = "Dominance_z:Gender"),
                      prior(normal(0, 1), class = "b", coef = "Gender:Leadership_z"), 
                      prior(normal(0, 1), class = "b", coef = "Gender:Prestige_z"),
                      prior(normal(0, 1), class = "b", coef = "Dominance_z"),
                      prior(normal(0, 1), class = "b", coef = "Leadership_z"),
                      prior(normal(0, 1), class = "b", coef = "Prestige_z")), save_all_pars = T)

summary(dm4)

dm4_hdi <- bayestestR::hdi(dm4, effects = "fixed", component = "conditional", ci = .95)
dm4_hdi[sign(dm4_hdi$CI_low) == sign(dm4_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')]

dm5 <- brm(Justification ~ Dominance_z * Realism_z * Content * Gender + Prestige_z * Realism_z * Content * Gender + Leadership_z * Gender * Realism_z * Content + SJS_z + SRPS_z + SSES_z + Spite_z * Content +  (1|Vignette) + (1|subjectID), control = list(adapt_delta = 0.99), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = c(prior(normal(0, 1), class = "Intercept"),
                      prior(normal(0, 1), class = "b", coef = "Dominance_z"),
                      prior(normal(0, 1), class = "b", coef = "Leadership_z"),
                      prior(normal(0, 1), class = "b", coef = "Prestige_z"),
                      prior(normal(3, 1), class = "b", coef = "Dominance_z:Gender"),
                      prior(normal(0, 1), class = "b", coef = "Gender:Leadership_z"), 
                      prior(normal(0, 1), class = "b", coef = "Gender:Prestige_z")), save_all_pars = T)

summary(dm5)

loo(dm1, dm2, dm4, dm5)
```

### DoPL motives predicting risky behavior (by content) in addition to spitefulness HDI

```{r Bayesian Analysis HDI, message=FALSE, warning=FALSE}
dm5_hdi <- bayestestR::hdi(dm5, effects = "fixed", component = "conditional", ci = .95)
kable(dm5_hdi[sign(dm5_hdi$CI_low) == sign(dm5_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')], format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)


```




### Bayesian analysis m4

```{r}
summary(m4)

m4_hdi <- bayestestR::hdi(m4, effects = "fixed", component = "conditional", ci = .95)
kable(m4_hdi[sign(m4_hdi$CI_low) == sign(m4_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')] , format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)
```

```{r, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
m5 <- brm(Justification ~ Dominance_z + Leadership_z + Prestige_z + (1|Vignette) + (1|subjectID), data = analysisDF,warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, prior = c(prior(normal(0,1), class = 'Intercept'),
                   prior(normal(0,1), class = 'b')))
summary(m5)

m5_gen <- brm(Justification_z ~ Dominance_z*Gender + Leadership_z*Gender + Prestige_z*Gender + (1|Vignette) + (1|subjectID), data = analysisDF, warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, 
  prior = c(prior(normal(0,1), class = 'Intercept'), 
                   prior(normal(3, 1), class = 'b', coef = "Dominance_z:Gender"),
                   prior(normal(0, 1), class = 'b', coef = "Gender:Leadership_z"),
                   prior(normal(0, 1), class = 'b', coef = "Gender:Prestige_z")),
                   save_all_pars = T)
summary(m5_gen)

```

### DoPL and Justification

```{r}
summary(m5_gen)

m5_gen_hdi <- bayestestR::hdi(m5_gen, effects = "fixed", component = "conditional", ci = .95)
kable(m5_gen_hdi[sign(m5_gen_hdi$CI_low) == sign(m5_gen_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')] , format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)


```

### Spite and DoPL

```{r Exploratory Analyses, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
m7 <- brm(Spite_z ~ Dominance_z*Gender + Leadership_z*Gender + Prestige_z*Gender, data = analysisDF, warmup = 500, iter = 8000, chains = 4, cores = 6,
          prior = c(prior(normal(0, 1), class = "Intercept"),
                   prior(normal(3, 1), class = "b", coef = "Dominance_z:Gender"),
                   prior(normal(0, 1), class = 'b', coef = "Gender:Leadership_z"),
                   prior(normal(0, 1), class = 'b', coef = "Gender:Prestige_z")),
                   save_all_pars = T)

```


```{r Exploratory Analyses HDI}
m7_hdi <- bayestestR::hdi(m7, effects = "fixed", component = "conditional", ci = .95)
kable(m7_hdi[sign(m7_hdi$CI_low) == sign(m7_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')] , format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)

summary(m7)
```

### DoPL and Measures

```{r DoPL and measures, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
m8 <- brm(mvbind(Dominance, Prestige, Leadership) ~ Spite_z + SSES + SRPS + SJS, data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6, 
          prior = c(prior(normal(0, 1), class = "Intercept")), save_all_pars = T)

```


```{r DoPL and measures HDI}

summary(m8)

m8_hdi <- bayestestR::hdi(m8, effects = "fixed", component = "conditional", ci = .95)
kable(m8_hdi[sign(m8_hdi$CI_low) == sign(m8_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')] , format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)

```

### DoPL and Measures * Gender
```{r m8 with gender interaction, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
m8_gen <- brm(mvbind(Dominance, Prestige, Leadership) ~ Spite_z*Gender + SSES*Gender + SRPS*Gender + SJS*Gender, data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6, 
          prior = c(prior(normal(0, 1), class = "Intercept")), save_all_pars = T)


```


```{r m8 with gender interaction HDI}
m8_gen_hdi <- bayestestR::hdi(m8_gen, effects = "fixed", component = "conditional", ci = .95)
kable(m8_gen_hdi[sign(m8_gen_hdi$CI_low) == sign(m8_gen_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')] , format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)

summary(m8_gen)

```

### DoPL and Measures * Age

```{r m8*Age, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
m8_Age <- brm(mvbind(Dominance, Prestige, Leadership) ~ Spite_z*Age + SSES*Age + SRPS*Age + SJS*Age, data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6, 
          prior = c(prior(normal(0, 1), class = "Intercept")), save_all_pars = T)

```


```{r m8*Age HDI}
m8_Age_hdi <- bayestestR::hdi(m8_Age, effects = "fixed", component = "conditional", ci = .95)
kable(m8_Age_hdi[sign(m8_Age_hdi$CI_low) == sign(m8_Age_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')] , format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)

summary(m8_Age)
```

# Justification and Content type

```{r message=FALSE, warning=FALSE}

ggplot(analysisDF, aes(y = Justification, x = Vignette, fill = Content, group = Vignette)) +
       geom_violin() +  
  scale_shape_prism() + 
  scale_y_continuous(guide = "prism_offset") + 
  scale_x_discrete(guide = "prism_offset")

timstop <- 2 + 3

```
# Demographic Information


```{r message=FALSE, warning=FALSE}
ggplotimage <- ggplot(experiment_two_DS, aes(x = Age)) + 
  geom_histogram(stat = "count") +
scale_fill_gradient("Count", low = "#FFEDA0", high = "#800F26")  + aes(fill = ..count..) + scale_shape_prism() + scale_y_continuous(limits = c(0, 10), guide = "prism_offset") + scale_x_continuous(guide = "prism_offset")
```

```{r Demographic table, message=FALSE, warning=FALSE, include=FALSE}

demo_table_1 <- experiment_two_DS[, demographicQuestions]

demo_table_1 <- demo_table_1 %>% mutate(Gender = case_when(
demo_table_1$Gender == 0 ~ "Male",
demo_table_1$Gender == 1 ~  "Female"
)) %>% mutate(Ethnicity = case_when(
  demo_table_1$Ethnicity == 0 ~ "Prefer not to answer",
demo_table_1$Ethnicity == 1 ~ "White",
demo_table_1$Ethnicity == 2 ~ "Mixed or Multiple ethnic origins",
demo_table_1$Ethnicity == 3 ~ "Asian or Asian Scottish or Asian British",
demo_table_1$Ethnicity == 4 ~ "African",
demo_table_1$Ethnicity == 5 ~ "Caribbean or Black",
demo_table_1$Ethnicity == 6 ~ "Arab",
demo_table_1$Ethnicity == 7 ~ "Other ethnic group"
)) %>% mutate(Eth.ori = case_when(
  demo_table_1$Eth.ori == 0 ~ "Prefer not to answer",
demo_table_1$Eth.ori == 1 ~ "Scottish",
demo_table_1$Eth.ori == 2 ~ "English",
demo_table_1$Eth.ori == 3 ~ "European" ,
demo_table_1$Eth.ori == 4 ~ "Latin American",
demo_table_1$Eth.ori == 5 ~ "Asian",
demo_table_1$Eth.ori == 6 ~ "Arab",
demo_table_1$Eth.ori == 7 ~ "African",
demo_table_1$Eth.ori == 8 ~ "Other"
)) %>% mutate(Edu = case_when(
demo_table_1$Edu == 0 ~ "Prefer not to answer",
demo_table_1$Edu == 1 ~ "Primary School",
demo_table_1$Edu == 2 ~ "GCSes or Equivalent",
demo_table_1$Edu == 3 ~ "A-Levels or Equivalent",
demo_table_1$Edu == 4 ~ "University Undergraduate Program",
demo_table_1$Edu == 5 ~ "University Post-Graduate Program",
demo_table_1$Edu == 6 ~ "Doctoral Degree"
))


options(digits = 2)
demo_names <- matrix(1:24, nrow = 24)
  for (i in names(demo_table_1)){
  if(is.numeric(demo_table_1[[i]])){
    options(digits = 2)
    demo_table_1_sd <- sd(demo_table_1$Age)
    demo_table_1_mean <- mean(demo_table_1$Age)
    demo_table_1_median <- median(demo_table_1$Age)
    demo_table_1_min <- min(demo_table_1$Age)
    demo_table_1_max <- max(demo_table_1$Age)
    age_demo_table_1 <- data.frame("Mean (SD)", demo_table_1_mean, demo_table_1_sd)
    age_demo_table_2 <- data.frame("Median [Min, Max]", demo_table_1_median, demo_table_1_min, demo_table_1_max)
    age_demo_table_2$Freq <- paste0(age_demo_table_2$demo_table_1_median, " [", age_demo_table_2$demo_table_1_min, ",", age_demo_table_2$demo_table_1_max, "]")
    age_demo_table_2 <- age_demo_table_2[, -c(2:4)]
    age_demo_table_1$Freq <- paste0(round(age_demo_table_1$demo_table_1_mean, digits = 2), " (", round(age_demo_table_1$demo_table_1_sd, digits = 2), ")")
    age_demo_table_1 <- age_demo_table_1[, -c(2:3)]
    colnames(age_demo_table_1) <- c("Var1", "new")
colnames(age_demo_table_2) <- c("Var1", "new")
    }
  for (i in colnames(demo_table_1)){
 
 if(!is.numeric(demo_table_1[[i]])){
   options(digits = 2)
     Education_Table <- data.frame(table(demo_table_1$Edu))
     Education_Table_percentage <- data.frame(sprintf("(%.1f%%)",round(prop.table(table(demo_table_1$Edu))*100, 3)))
     colnames(Education_Table_percentage) <- "Freq"
     Ethnicity_Table <- data.frame(table(demo_table_1$Ethnicity))
     Ethnicity_Table_percentage <- data.frame(sprintf("(%.1f%%)",round(prop.table(table(demo_table_1$Ethnicity))*100, 3)))
      colnames(Ethnicity_Table_percentage) <- "Freq"
     Ethnic_Origin_Table <- data.frame(table(demo_table_1$Eth.ori))
     Ethnic_Origin_Table_percentage <- data.frame(sprintf("(%.1f%%)",round(prop.table(table(demo_table_1$Eth.ori))*100, 3)))
      colnames(Ethnic_Origin_Table_percentage) <- "Freq"
     Gender_Table <- data.frame(table(demo_table_1$Gender))
     Gender_Table_percentage <- data.frame(sprintf("(%.1f%%)",round(prop.table(table(demo_table_1$Gender))*100, 3)))
      colnames(Gender_Table_percentage) <- "Freq"
 }
  }
  }

options(digits = 2)
demographic_table <- rbind(Gender_Table, Education_Table, Ethnic_Origin_Table, Ethnicity_Table)
demographic_table_percentage <- rbind(Gender_Table_percentage, Education_Table_percentage, Ethnic_Origin_Table_percentage, Ethnicity_Table_percentage)
demographic_table["Percentage"] <- demographic_table_percentage["Freq"]
demographic_table$new <- paste(demographic_table$Freq, demographic_table$Percentage)

demographic_table <- demographic_table[, -c(2:3)]
demographic_table <- rbind(age_demo_table_1, age_demo_table_2, demographic_table)
```

```{r}
kable(demographic_table, format = "html", bootabs = T, escape = F, longtable = T,
      col.names = c("", "Overall *n* = 92"),
      align = c("l", "c"),
      caption = "*Participant Demographic Information*") %>%
  kable_styling(full_width = F)%>%
  row_spec(row = 0, align = "c")%>%
  column_spec(column = 1, width = "1.5in" )%>%
  column_spec(column = 2, width = "1in") %>%
  pack_rows("Age",1, 2 )%>%
  pack_rows("Gender", 3, 4)%>%
  pack_rows("Ethnicity", 11, 17)%>%
  pack_rows("Ethnic Origin", 18, 22)%>%
  pack_rows("Educational Attainment", 5, 10)

```



demographic_table <- demographic_table[c(1, 2, 3, 4, 18, 13, 14, 15, 12, 11, 17, 16, 8, 6, 5, 9, 10, 7, 22, 20, 19, 21), ]
rownames(demographic_table) <- NULL
saveRDS(demographic_table, "demographic_table.rds")

demographic_table <- demographic_table[c(1:12), ]