---
title: "Experiment 2 Analysis"
author: "Andrew Ithurburn"
date: "23/06/2021"
output: 
   html_document: 
     toc: yes
     toc_float:
       smooth_scroll: yes
     code_folding: hide
     fig_caption: yes
     number_sections: yes
     css: table_styling.css
     theme: paper
editor_options: 
  chunk_output_type: inline
---
# Experiment 2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DT)
library(ggplot2)
library(ggthemes)
library(tidyverse)
library(papaja)
library(brms)
library(rstan)
library(bayestestR)
library(sjPlot)
library(psych)
library(BayesFactor)
library(bayesplot)
library(kableExtra)
library(ggcorrplot)
library(ggprism)
options(mc.corrs = parallel::detectCores()) # can run chains in parallel with each other
rstan_options(auto_write = TRUE)
options(control = list(adapt_delta = 0.99999))
options(brms.backend = "cmdstanr")
source("prior_function_file.R")
source("Priors.R")
bayesplot::bayesplot_theme_set(theme_apa())
locfunc <- function(data, to){
  which(colnames({{data}})=={{to}})
}

lfunc <- function(dataset, to, from) {
  loc1 <- which(colnames({{dataset}}) == {{to}})
  loc2 <- which(colnames({{dataset}}) == {{from}})
  length({{dataset}}[loc1:loc2])
}
theme_set(theme_apa(base_size = 12))

```

```{r message=FALSE, warning=FALSE, include=FALSE}
experiment_two_DS_time <- read.csv("Experiment_2_Dataset_clean.csv")
experiment_two_DS <- read.csv("Experiment_2_Dataset_clean_noTime.csv")
df1 <- read.csv("df1.csv")
corr_table <- readRDS("corr_table.rds")
m4 <- readRDS("m4.rds")
m5 <- readRDS("m5.rds")
m5_gen <- readRDS("m5_gen.rds")
m7 <- readRDS("m7.rds")
m8 <- readRDS("m8.rds")
m8_gen <- readRDS("m8_gen.rds")
m8_Age <- readRDS("m8_Age.rds")
dm0 <- readRDS("dm0.rds")
dm1 <- readRDS("dm1.rds")
dm2 <- readRDS("dm2.rds")
dm3 <- readRDS("dm3.rds")
dm4 <- readRDS("dm4.rds")
dm5 <- readRDS("dm5.rds")
demographic_table <- readRDS("demographic_table.rds")
m2prior <- readRDS("m2prior.rds")
dopl_1_prior <- readRDS("m4prior.rds")
m7prior <- readRDS("m7prior.rds")
m1_intPrior <- readRDS("m1_intPrior.rds")
analysisDF <- read.csv("analysisDF.csv")
demographicQuestions <- c("Age", "Gender", "Ethnicity", "Eth.ori", "Edu")
sjsQuestions <- c("SJS.1", "SJS.2", "SJS.3")
srpsQuestions <- c("SRPS.1"
, "SRPS.2"
, "SRPS.3"
, "SRPS.4"
, "SRPS.5"
, "SRPS.6"
, "SRPS.7"
, "SRPS.8"
, "SRPS.9"
, "SRPS.10"
, "SRPS.11"
, "SRPS.12"
, "SRPS.13"
, "SRPS.14"
, "SRPS.15"
, "SRPS.17"
, "SRPS.18"
, "SRPS.19"
, "SRPS.20"
, "SRPS.21"
, "SRPS.22"
, "SRPS.23"
, "SRPS.24")

srps.rcQuestions <- c("SRPS.1"
, "SRPS.2"
, "SRPS.3"
, "SRPS.4"
, "SRPS.5"
, "SRPS.6"
, "SRPS.7"
, "SRPS.8"
, "SRPS.9"
, "SRPS.10"
, "SRPS.11"
, "SRPS.12"
, "SRPS.13"
, "SRPS.14"
, "SRPS.15")

srps.dmQuestions <- c("SRPS.17"
, "SRPS.18"
, "SRPS.19"
, "SRPS.20"
, "SRPS.21"
, "SRPS.22"
, "SRPS.23"
, "SRPS.24")

ssesQuestions <- c("SSES.1"
, "SSES.2"
, "SSES.3"
, "SSES.4"
, "SSES.5"
, "SSES.6"
, "SSES.7"
, "SSES.8"
, "SSES.9"
, "SSES.10")

spiteQuestions <- c("Spite.1"
, "Spite.2"
, "Spite.3"
, "Spite.4"
, "Spite.5"
, "Spite.6"
, "Spite.7"
, "Spite.8"
, "Spite.9"
, "Spite.10"
, "Spite.11"
, "Spite.12"
, "Spite.13"
, "Spite.14"
, "Spite.15"
, "Spite.16")

Vign.Sex <- c("Vign.1", "Vign.2", "Vign.4", "Vign.7", "Vign.10")
Vign.noSex <- c("Vign.3", "Vign.5", "Vign.6", "Vign.8", "Vign.9")
Vign.Overall <- c("Vign.1", "Vign.2", "Vign.4", "Vign.7", "Vign.10", "Vign.3", "Vign.5", "Vign.6", "Vign.8", "Vign.9")

Real.Sex <- c("Real.1", "Real.2", "Real.4", "Real.7", "Real.10")
Real.noSex <- c("Real.3", "Real.5", "Real.6", "Real.8", "Real.9")
Real.Overall <- c("Real.1", "Real.2", "Real.4", "Real.7", "Real.10", "Real.3", "Real.5", "Real.6", "Real.8", "Real.9")

doplQuestions <- c('DoPL_1', 'DoPL_6', 'DoPL_11', 'DoPL_13', 'DoPL_14', 'DoPL_16', 'DoPL_5', 'DoPL_7', 'DoPL_8', 'DoPL_12', 'DoPL_17', 'DoPL_18', 'DoPL_2', 'DoPL_3', 'DoPL_4', 'DoPL_9', 'DoPL_10', 'DoPL_15')

dominanceQuestions <- c('DoPL_2','DoPL_3','DoPL_4','DoPL_9','DoPL_10','DoPL_15')
prestigeQuestions <- c('DoPL_5','DoPL_7','DoPL_8','DoPL_12','DoPL_17','DoPL_18')
leadershipQuestions <- c('DoPL_1','DoPL_6','DoPL_11','DoPL_13','DoPL_14','DoPL_16')

UMSQuestions <- c('UMS_1', 'UMS_2', 'UMS_3', 'UMS_4','UMS_5','UMS_6','UMS_7','UMS_8','UMS_9','UMS_11', 'UMS_12')
UMSIntimacyQuestions <- c('UMS_11', 'UMS_12')
UMSAffiliationQuestions <- c('UMS_1', 'UMS_2', 'UMS_3', 'UMS_4','UMS_5','UMS_6','UMS_7','UMS_8','UMS_9')

savedQuestionsBefore <- c('subjectID', "Age", "Duration..in.seconds.", "Gender", "Ethnicity", "Eth.ori", "Edu",
                     "DoPLSum"
,"dominanceSum"
,"prestigeSum"
,"leadershipSum"
,"UMSSum"
,"UMSIntimacySum"
,"UMSAffiliationSum"
,"sjsSum"
,"ssesSum"
, "Spite"
,"Vign.Sex"
,"Vign.noSex"
,"Vign.Ovr.Score"
,"Real.Sex"
,"Real.noSex"
,"Real.Ovr.Score"
,"srps.rc.rescale"
,"srps.dm.rescale"
,"srps.sum.rescale",
"Power",
"Vign.1",
"Vign.2",
"Vign.3",
"Vign.4",
"Vign.5",
"Vign.6",
"Vign.7",
"Vign.8",
"Vign.9",
"Vign.10",
"Real.1",
"Real.2",
"Real.3",
"Real.4",
"Real.5",
"Real.6",
"Real.7",
"Real.8",
"Real.9",
"Real.10")

savedQuestionsAfter <- c('subjectID', "Age", "Duration..in.seconds.", "Gender", "Ethnicity", "Eth.ori", "Edu",
                     "DoPLSum"
,"dominanceSum"
,"prestigeSum"
,"leadershipSum"
,"UMSSum"
,"UMSIntimacySum"
,"UMSAffiliationSum"
,"sjsSum"
,"ssesSum"
, "Spite"
,"Vign.Sex"
,"Vign.noSex"
,"Vign.Ovr.Score"
,"Real.Sex"
,"Real.noSex"
,"Real.Ovr.Score"
,"srps.rc.rescale"
,"srps.dm.rescale"
,"srps.sum.rescale"
,"Content",
"Vignette",
"Justification",
"Realism",
"Power")
```

# Experiment 1 Demographics

```{r echo=TRUE, message=FALSE, warning=FALSE}
kable(demographic_table, format = "html", bootabs = T, escape = F, longtable = T,
      col.names = c("", "Overall *n* = 92"),
      align = c("l", "c"),
      caption = "*Participant Demographic Information*") %>%
  kable_styling(full_width = F)%>%
  row_spec(row = 0, align = "c")%>%
  column_spec(column = 1, width = "1.5in" )%>%
  column_spec(column = 2, width = "1in") %>%
  pack_rows("Age",1, 2 )%>%
  pack_rows("Gender", 3, 4)%>%
  pack_rows("Ethnicity", 11, 17)%>%
  pack_rows("Ethnic Origin", 18, 22)%>%
  pack_rows("Educational Attainment", 5, 10)

```

## DoPL motives predicting risky behavior (by content) ggplot {.tabset}

### Dominance

```{r}
ggplot(analysisDF, aes(x = Dominance, y = Justification, col = Content)) + 
  geom_point(size = .7,
             alpha = .8,
             position = "jitter") + 
  geom_smooth(method = "lm", 
              se = F,
              size = 2, 
              alpha = .8)
```

### Prestige
```{r}
ggplot(analysisDF, aes(x = Prestige, y = Justification, col = Content)) + 
  geom_point(size = .7,
             alpha = .8,
             position = "jitter") + 
  geom_smooth(method = "lm", 
              se = F,
              size = 2, 
              alpha = .8)
```

### Leadership
```{r}
ggplot(analysisDF, aes(x = Leadership, y = Justification, col = Content)) + 
  geom_point(size = .7,
             alpha = .8,
             position = "jitter") + 
  geom_smooth(method = "lm", 
              se = F,
              size = 2, 
              alpha = .8)
```

### Spitefulness
```{r}
ggplot(analysisDF, aes(x = Spite, y = Justification, col = Content)) + 
  geom_point(size = .7,
             alpha = .8,
             position = "jitter") + 
  geom_smooth(method = "lm", 
              se = F,
              size = 2, 
              alpha = .8) 
```

# Initial Bayesian Analysis

```{r Bayesian, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}



m0 <- brm(Justification_z ~ 1 + (1|Vignette) + (1|subjectID), data = analysisDF, 
         warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, save_all_pars = T,
          prior = prior_m0)

# models 
m1 <- brm(Justification_z ~ Spite_z * Content + (1|Vignette) + (1|subjectID), data = analysisDF, 
        warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, save_all_pars = T,
         prior = prior_m1)
summary(m1) 

m2 <- brm(Justification ~ Spite_z * Content + Realism_z + (1|Vignette) + (1|subjectID), data = analysisDF, 
        warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 4, save_all_pars = T,
         prior = prior_m2)
summary(m2)

m3 <- brm(Justification ~ Spite_z * Content + Realism_z + SSES + SRPS + SJS + (1|Vignette) + 
           (1|subjectID), data = analysisDF,warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, 
         save_all_pars = T,
         prior = prior_m3)
summary(m3)

m4 <- brm(Justification ~ Spite_z * Content * Realism_z + SSES_z + SRPS_z + SJS_z + (1|Vignette) + 
           (1|subjectID), data = analysisDF,warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, 
         save_all_pars = T,
         prior = prior_m4)

```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
experiment_1_priors <- prior_function(m2prior)
dopl_1_priors <- prior_function(m7prior)
m1_intPrior <- prior_function(m1_intPrior)
print(experiment_1_priors)

```


## Bayesian Correlation

```{r, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
scale_corr <- brm(mvbind(SSES, SRPS, Spite, SJS, Dominance, Prestige, Leadership) ~ 1, data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6, 
                  prior = c(prior(normal(0, 1), class = "Intercept")), save_all_pars = T)
cor_1 <- summary(scale_corr)
corr_table <- cor_1[["rescor_pars"]]
```


```{r}
kable(corr_table, format = "html", booktabs = T, escape = F, longtabe = F, digits = 2, col.names = c('Estimate',	'Est.Error',	'l-95% CI',	'u-95% CI',	'Rhat',	'Bulk_ESS',	'Tail_ESS')) %>%
  kable_styling(full_width = F)  %>%
  remove_column(6:8)
```

## DoPL motives predicting risky behavior (by content) in addition to spitefulness

```{r Bayesian Analysis, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
dm0 <- brm(Justification ~ 1 + (1|Vignette) + (1|subjectID), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = prior_dm0, save_all_pars = T)

summary(dm0)

dm1 <- brm(Justification ~ Dominance_z * Gender + Prestige_z * Gender + Leadership_z * Gender + (1|Vignette) + (1|subjectID), data = analysisDF, iter = 8000,control = list(adapt_delta = 0.99), warmup = 500, chains = 4, cores = 6
           ,prior = prior_dm1, save_all_pars = T)

summary(dm1)

dm3 <- brm(Justification ~ Dominance_z * Gender + Prestige_z * Gender + Leadership_z * Gender + Age + (1|Vignette) + (1|subjectID), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = c(prior(normal(0, 1), class = "Intercept")), save_all_pars = T)

summary(dm3)

dm2 <- brm(Justification ~ Dominance_z * Gender + Prestige_z * Gender + Leadership_z * Gender + SJS_z + SRPS_z + SSES_z + Spite_z +  (1|Vignette) + (1|subjectID), control = list(adapt_delta = 0.99), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = prior_dm2, save_all_pars = T)

summary(dm2)

dm4 <- brm(Justification ~ Dominance_z * Gender * Content + Prestige_z * Gender * Content + Leadership_z * Gender * Content + SJS_z + SRPS_z + SSES_z + Spite_z +  (1|Vignette) + (1|subjectID), control = list(adapt_delta = 0.99), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = prior_dm4, save_all_pars = T)

summary(dm4)

dm4_hdi <- bayestestR::hdi(dm4, effects = "fixed", component = "conditional", ci = .95)
dm4_hdi[sign(dm4_hdi$CI_low) == sign(dm4_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')]


dm5 <- brm(Justification ~ Dominance_z * Realism_z * Content * Gender + Prestige_z * Realism_z * Content * Gender + Leadership_z * Gender * Realism_z * Content + Spite_z * Content +  (1|Vignette) + (1|subjectID), control = list(adapt_delta = 0.99), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6
           ,prior = prior_dm5, save_all_pars = T)

summary(dm5)

bm4 <- brm(Justification ~ Dominance_z * Realism_z * Content * Gender + Prestige_z * Realism_z * Content * Gender + Leadership_z * Realism_z * Content * Gender + Spite_z * Content * Gender + (1|Vignette) + (1|subjectID), control = list(adapt_delta = 0.99), data = analysisDF, iter = 8000, warmup = 500, chains = 4, cores = 6, save_all_pars = T)

loo(dm1, dm2, dm4, dm5)
```

## DoPL motives predicting risky behavior (by content) in addition to spitefulness HDI

```{r Bayesian Analysis HDI, message=FALSE, warning=FALSE}
dm5_hdi <- bayestestR::hdi(dm5, effects = "fixed", component = "conditional", ci = .95)
kable(dm5_hdi[sign(dm5_hdi$CI_low) == sign(dm5_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')], format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)


```





## Bayesian analysis m4

```{r}
summary(m4)

m4_hdi <- bayestestR::hdi(m4, effects = "fixed", component = "conditional", ci = .95)
kable(m4_hdi[sign(m4_hdi$CI_low) == sign(m4_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')] , format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)
```

```{r, eval = F, message=FALSE, warning=FALSE, class.source = "fold-show"}
m5 <- brm(Justification ~ Dominance_z + Leadership_z + Prestige_z + (1|Vignette) + (1|subjectID), data = analysisDF,warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, prior = c(prior(normal(0,1), class = 'Intercept'),
                   prior(normal(0,1), class = 'b')))
summary(m5)

m5_gen <- brm(Justification_z ~ Dominance_z*Gender + Leadership_z*Gender + Prestige_z*Gender + (1|Vignette) + (1|subjectID), data = analysisDF, warmup = 500, control = list(adapt_delta = 0.95), iter = 8000, chains = 4, cores = 6, 
  prior = c(prior(normal(0,1), class = 'Intercept'), 
                   prior(normal(3, 1), class = 'b', coef = "Dominance_z:Gender"),
                   prior(normal(0, 1), class = 'b', coef = "Gender:Leadership_z"),
                   prior(normal(0, 1), class = 'b', coef = "Gender:Prestige_z")),
                   save_all_pars = T)
summary(m5_gen)

```

## DoPL and Justification

```{r}
summary(m5_gen)

m5_gen_hdi <- bayestestR::hdi(m5_gen, effects = "fixed", component = "conditional", ci = .95)
kable(m5_gen_hdi[sign(m5_gen_hdi$CI_low) == sign(m5_gen_hdi$CI_high),
            c('Parameter', 'CI','CI_low', 'CI_high')] , format = "html", booktabs = T, escape = F, longtable = F, digits = 2) %>% kable_styling(full_width = T)


```
